---
title: "modelos iniciais 1"
author: "Renan Machado"
date: "2024-04-11"
output: html_document
---
 
#Pacotes ultilizados
```{r}
library(ltm)
library(readxl)
#library(mirt)
library(tidyverse)
library(psych)
library(polycor)
library(mirt)
```

```{r}
dados_25_03 <- read_excel("dados_25_03.xlsx")
```

```{r}
fit2 <- grm(dados_25_03)
```

```{r}
a <- plot(fit2,items = 1, lwd = 2, cex = 1.2, legend = TRUE, cx = "left",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)

a
```


```{r}
# Curvas são produzidas

par(mfrow = c(2, 2))
plot(fit2, lwd = 2, cex = 1.2, legend = TRUE, cx = "left",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)
```


# tipo = "IIC"
```{r}
plot(fit2, type = "IIC", lwd = 2, cex = 1.2, legend = TRUE, cx = "topleft",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)
```


```{r}
par(mfrow = c(2, 2))
for (i in 1:24) {
  plot(fit2, type = "IIC", items = i, lwd = 2, cex = 1.2, legend = TRUE, cx = "topleft",
       xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)
}

```


# para a curva de informações do teste, precisamos especificar novamente `items = 0'
```{r}
plot(fit2, type = "IIC", items = 0, lwd = 2, xlab = "Latent Trait",
     cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)
```


# As curvas características da categoria de resposta ao item podem ser plotadas
# para cada categoria de resposta separadamente como segue
```{r}
par(mfrow = c(2, 2))
plot(fit2, category = 1, lwd = 2, cex = 1.2, legend = TRUE, cx = -4.5,
     cy = 0.85, xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3,
     cex.axis = 1.1)
for (ctg in 2:3) {
      plot(fit2, category = ctg, lwd = 2, cex = 1.2, annot = FALSE,
           xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3,
           cex.axis = 1.1)
}
```


####################
# Informações sobre o item 
```{r}
information(fit2, c(-4, 4))

information(fit2, c(-4, 4), items = c(1, 6))
```

#### NOVAS ATUALIZAÇÕES 23/04


```{r}
dados_edit1 <- dados_25_03 %>%
  mutate(
    s2 = case_when(
      is.na(s2) ~ NA_real_,
      s2 == 2 ~ 1,
      TRUE ~ 0
    ),
    c3 = case_when(
      is.na(c3) ~ NA_real_,
      c3 == 2 ~ 1,
      TRUE ~ 0
    )
  )%>%
  select(-f1)
```



```{r}
fit3 <- grm(dados_edit1)
```

```{r}
c <- plot(fit3,items = 1, lwd = 2, cex = 1.2, legend = TRUE, cx = "left",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)

c
```

```{r}
# Curvas são produzidas

par(mfrow = c(2, 2))
plot(fit3, lwd = 2, cex = 1.2, legend = TRUE, cx = "left",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)
```

```{r}
plot(fit3, type = "IIC", lwd = 2, cex = 1.2, legend = TRUE, cx = "topleft",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)
```

















parametros de cada curva caracteristica com 3 parametros um theta um b e um alpha.
```{r}
fit4 <- grm(data = dados_25_03)

# Obtendo os valores de theta para cada indivíduo
theta <- factor.scores(fit4)

# Exibindo os valores de theta
print(theta)
```

```{r}
fit4 <- ltm::grm(dados_edit1)

# Calcular os escores fatoriais
theta1 <- ltm::factor.scores(fit4,resp.patterns = dados_edit1)

print(theta1)
```


```{r}

summary(fit3)
parametros <- coef(fit3)

# Exibir os resultados
print(parametros)

```
```{r}
vetor= dados_edit1[1,]
factor.scores(fit3, resp.patterns= vetor)

```


```{r}
calcular_alfa_cronbach <- function(dados_edit1) {
  # Remover NA
  dados_sem_na <- na.omit(dados_edit1)
  
  # NA
  if (nrow(dados_sem_na) < nrow(dados_edit1)) {
    warning("")
  }
  
  n_itens <- ncol(dados_sem_na)
  n_casos <- nrow(dados_sem_na)
  correlacao_itens <- cor(dados_sem_na)
  var_total_itens <- apply(dados_sem_na, 2, var)
  var_total_escores <- var(rowSums(dados_sem_na))
  
  #  coeficiente alfa de Cronbach
  alfa <- (n_itens / (n_itens - 1)) * (1 - sum(var_total_itens) / var_total_escores)
  
  return(alfa)
}
```


```{r}

coef_alfa <- calcular_alfa_cronbach(dados_edit1)
print(coef_alfa)

```


```{r}
?polychor.matrix

#polycor<- polychor.matrix(x,v)
```


```{r}
?simdata 
```


```{r}
#library(msm)
```

```{r}
#install.packages("http://www.est.ufmg.br/~msantos/mcurso2013_1.0.zip", repos = NULL, type = "source")
#library(mcurso2013)
```


```{r}
dados_edit2 <- dados_25_03 %>%
  mutate(
    s2 = case_when(
      is.na(s2) ~ NA_real_,
      s2 == 2 ~ 1,
      TRUE ~ 0
    ),
    c3 = case_when(
      is.na(c3) ~ NA_real_,
      c3 == 2 ~ 1,
      TRUE ~ 0
    )
  )%>%
  select(-f1)
```


```{r}
fit3 <- grm(dados_edit1)
```




```{r}


?graded
library(mirt)

data <- matrix(c(1, 1, 0, 0,
                 1, 0, 1, 1,
                 0, 1, 0, 0,
                 1, 1, 1, 1,
                 0, 0, 1, 0), 
               ncol = 4, byrow = TRUE)

model <- mirt(data, 
              model = "graded",  
              itemtype = "graded")

summary(model)
```












































































###################################################
### preliminaries
###################################################
library(ltm)
data(LSAT)
data(Environment)
data(WIRS)


###################################################
### Analysis of LSAT data set -- Section 3.1
###################################################

# descriptive statistics
descript(LSAT)


###########################
# constrained Rasch model #
###########################
fit1 <- rasch(LSAT, constraint = cbind(length(LSAT) + 1, 1))
summary(fit1)

# coefficients and conditional proabibilities
coef(fit1, prob = TRUE, order = TRUE)

# Goodness-of-Fit using Bootstrap
GoF.rasch(fit1, B = 199)

# Goodness-of-Fit in the margins
margins(fit1)
margins(fit1, type = "three-way", nprint = 2)


#############################
# unconstrained Rasch model #
#############################
fit2 <- rasch(LSAT)
summary(fit2)

# likelihood ratio test between constrained and unconstrained models
anova(fit1, fit2)

# fit of the three-way margins
margins(fit2, type = "three-way", nprint = 2)


##############
# Extensions #
##############

# Two-Parameter Logistic model
fit3 <- ltm(LSAT ~ z1)
anova(fit2, fit3)

# Rasch model with guessing parameter
fit4 <- tpm(LSAT, type = "rasch", max.guessing = 1)
anova(fit2, fit4)


#############################################
# Item Charecteristc and Information Curves #
#############################################

# put all plots in one figure
par(mfrow = c(2, 2))

# by default the Item Characteristic Curves are plotted;
# we include a legend
plot(fit2, legend = TRUE, cx = "bottomright", lwd = 3,
     cex.main = 1.5, cex.lab = 1.3, cex = 1.1)

# to plot the Item Information Curves the `type' argument is used;
# since we included a legend in the ICCs plot no extra annotation is
# required --> `annot = FALSE'
plot(fit2, type = "IIC", annot = FALSE, lwd = 3, cex.main = 1.5,
     cex.lab = 1.3)

# the Test Information Curve is plotted by using both `type = "IIC"'
# and `items = 0'
plot(fit2, type = "IIC", items = 0, lwd = 3, cex.main = 1.5,
     cex.lab = 1.3)

# we also include the amount of Test information in the intervals
# (-4, 0) and (0, 4)
plot(0:1, 0:1, type = "n", ann = FALSE, axes = FALSE)
info1 <- information(fit2, c(-4, 0))
info2 <- information(fit2, c(0, 4))
text(0.5, 0.5, labels = paste("Total Information:", round(info1$InfoTotal, 3),
     "\n\nInformation in (-4, 0):", round(info1$InfoRange, 3),
     paste("(", round(100 * info1$PropRange, 2), "%)", sep = ""),
     "\n\nInformation in (0, 4):", round(info2$InfoRange, 3),
     paste("(", round(100 * info2$PropRange, 2), "%)", sep = "")), cex = 1.5)


#####################################
# Factor Scores - Ability Estimates #
#####################################

# ability estimates for the observed response patterns
factor.scores(fit2)

# ability estimates for specific response patterns
factor.scores(fit2, resp.patterns = rbind(c(0,1,1,0,0), c(0,1,0,1,0)))




###################################################
### Analysis of Environment data set -- Section 3.2
###################################################

# descriptive statistics
descript(Environment)

rcor.test(Environment, method = "kendall")


#####################################
# constrained Graded Response Model #
#####################################
fit1 <- grm(Environment, constrained = TRUE)
fit1


# fit of the margins
margins(fit1)
margins(fit1, type = "three")


#######################################
# unconstrained Graded Response Model #
#######################################
fit2 <- grm(Environment)
fit2

# likelihood ratio test between constrained and unconstrained models
anova(fit1, fit2)


#############################################
# Item Charecteristc and Information Curves #
#############################################

# produce 4 plots per page
par(mfrow = c(2, 2))

# again by default the Item Response Category Characterstic
# Curves are produced; we include a legend
plot(fit2, lwd = 2, cex = 1.2, legend = TRUE, cx = "left",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)

# the Item Information Curves are produced by specifying
# `type = "IIC"'
plot(fit2, type = "IIC", lwd = 2, cex = 1.2, legend = TRUE, cx = "topleft",
     xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)

# for the Test Information Curve we again need to specify `items = 0'
plot(fit2, type = "IIC", items = 0, lwd = 2, xlab = "Latent Trait",
     cex.main = 1.5, cex.lab = 1.3, cex.axis = 1.1)

# we also include the amount of Test information in the intervals
# (-4, 0) and (0, 4)
info1 <- information(fit2, c(-4, 0))
info2 <- information(fit2, c(0, 4))
text(-1.9, 8, labels = paste("Information in (-4, 0):",
     paste(round(100 * info1$PropRange, 1), "%", sep = ""),
     "\n\nInformation in (0, 4):",
     paste(round(100 * info2$PropRange, 1), "%", sep = "")), cex = 1.2)


# The Item Response Category Characteristic Curves can be plotted
# for each response category separately as follows
par(mfrow = c(2, 2))
plot(fit2, category = 1, lwd = 2, cex = 1.2, legend = TRUE, cx = -4.5,
     cy = 0.85, xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3,
     cex.axis = 1.1)
for (ctg in 2:3) {
      plot(fit2, category = ctg, lwd = 2, cex = 1.2, annot = FALSE,
           xlab = "Latent Trait", cex.main = 1.5, cex.lab = 1.3,
           cex.axis = 1.1)
}


####################
# Item Information #
####################
information(fit2, c(-4, 4))

information(fit2, c(-4, 4), items = c(1, 6))




###################################################
### Analysis of WIRS data set -- Section 4
###################################################

# Two-Factor and Interaction models
fit1 <- ltm(WIRS ~ z1 + z2)
fit2 <- ltm(WIRS ~ z1 * z2)
fit1
fit2

# likelihood ratio test
anova(fit1, fit2)








